Response to reviewers

### 2017-01-12 revision/response2.Rmd
More updates
Reviewer response with Alicia's edits

---
title: "Response to reviewers"
author: "Eric Hare, Heike Hofmann, Alicia Carriquiry"
date: "October 24, 2016"
output:
  pdf_document: default
bibliography: references.bib
---

@@

    **Most of the references that were suggested by reviewers earlier were incorporated into the revised version of the manuscript.  Regarding the "overlap" with Petraco's work, please see the attached document entitled x3prplus for an in-depth discussion of our use of exactly one function in Petraco's package.**

@@

    **First, it seems more appropriate to refer to Hoeksema's U statistic since she was the one to propose its use in her dissertation.  As the reviewer notes, this work was carried out in our own department, and we were well aware of it.  Thus our surprise with the review, since to say that our work is a repeat of Amy Hoeksema's work is so inaccurate as to make us wonder whether the reviewer is familiar with either approaches.  On October 11th, 2016, we sat down with Max Morris to discuss the similarities and differences between the Hoeksema U-statistic, and the methods used and features derived in our paper. Max was at least as surprised as we were to read the reviewer's comment, since the differences between Amy's work and ours are stark. The Hoeksema U-statistic characterizes toolmark signatures by producing two sets of correlation values. One set is produced by doing "coordinated shifts" after finding the ideal matching window, and computing each correlation value. The other set is computed by doing "independent shifts". When the two toolmarks match, we'd expect that the correlation values from the coordinated shifts would be significantly higher than those computed from the independent shifts, and this is assessed using a Mann-Whitney U statistic. While very interesting and worth further discussion, Max Morris agreed that this is far different from the methods we have proposed. In our work, we use full bullet signatures from pairs of bullets and extract several features based on these. The features include a cross-correlation, as well as the number of matching striae, the number of consecutive matching striae, the difference in the height of the signatures at each peak and at each valley, and several more. At no time is a Mann-Whitney U statistic used, windows extracted, or any coordinated/independent shifts used. These are completely different approaches where the only "similarity" is that we also compute a correlation, albeit between different variables!**

@@

    **The reviewer must have looked at the wrong code because no one who is reasonably familiar with R would claim that x3prplus is a "wrapper" for x3pr!  Please see the attached document for a rebuttal to these claims.  In x3prplus, all we did is call ONE of Petraco's functions, read.x3p, to read 3D files.  Everything else is completely different, as can be seen in the attached document. Perhaps our choice of name for the package has contributed to the confusion.**

@@

    **Really?  We have referred to many of those papers in the manuscript and have shown how our approach is quite different.  Indeed, even PCAST (the President's Council of Advisors in Science and Technology) in its report, mentioned that our work was the only promising work and they actually looked at all the literature themselves. So we respectfully disagree with Reviewer 2. The Riva and Champod paper published in 2014 is indeed referred to in the manuscript and of all the published work, it is the one that most resembles what we have done.  The reviewer poo-poos our saying that one difference is that Riva and Champod worked on casings and we worked on bullets.  The reviewer would be well advised to read our comment more carefully;  the reason it is important is that Riva and Champod make use of the circular structure of their data to pre-process their images and develop their score.  A big component of their algorithm is the alignment of images, which they do by rotating the images on the xY plane.  This is not something that cannot be extended to the case of bullets, were the XY plane is not flat and where rotation makes no sense.  The approach they use to extract features from the aligned images is completely different from ours and for the reviewer to say that we are re-inventing the wheel is a bit of a scandal.  The fact that Riva and Champod have come up with a nice automated algorithm to match breech face and firing pin images does not mean that we cannot come up with a DIFFERENT automated algorithm to match bullet lands. This said, we have added additional commentary about Riva and Champod in our manuscript.**

@@

    **We referenced the OpenFMC organization and devoted a paragraph to its discussion. This is the organization that is the recommended citation for the package which we use a function of, `x3pr`. We have added a reference to Dr. Petraco directly in this discussion. See the below citation, given by `x3pr` as of October 17th, 2016:**
    ```{r}
    citation("x3pr")
    ```

@@

    **We are very clear about the limitations presented by a small dataset, particularly in the conclusion. Unfortunately, this are the data that we had to work with. With that said, the idea of statistical modeling is that once new data are obtained, it will be rather trivial to compute the set of features used in our model, and retrain the model with a broader and more varied dataset. Whether performance on holdout samples would remain as strong remains to be seen. But because this code is open-source and in the public domain, the algorithm can be assessed on new data by anyone willing to invest the time to run it. While the dataset is small (only 10 barrels) we have been told by multiple firearm examiners that it is a challenging dataset on which to develop methods because the 10 barrels were consecutively manufactured. Thus, one would expect that thre striae made by those barrels will be more similar across them than across two randomly selected barrels from a large population. We are collaborating with Alan Zhang in NIST to assemble a larger database that will be publicly available within a year or two.**

@@

    **Did the reviewer read the correct paper?  The revised copy of our paper contains over thirty references, not just one. Many are from previous statistical studies on bullet matching (e.g., Biasotti 1959, Chu 2010, Riva 2014) while many more are references on statisitcal tests themselves (e.g., Therneau 2015, Liaw 2002, Cleveland 1979)**

@@

# x3prplus

>>>>

---
title: "Response to reviewers"
author: "Eric Hare, Heike Hofmann, Alicia Carriquiry"
date: "January 12, 2017"
output:
  pdf_document: default
bibliography: references.bib
---

@@

    **Most of the references that were suggested by reviewers earlier were incorporated into the revised version of the manuscript.  Regarding the "overlap" with Petraco's work, please see the attached document entitled x3prplus for an in-depth discussion of our use of exactly one function in Petraco's package. To avoid further confusion, we are no longer using any of Petraco's functions and have instead published a 100% non-overlapping package called bulletr.**

@@

    **First, it seems more appropriate to refer to Hoeksema's U statistic since she was the one to propose its use in her dissertation.  As the reviewer notes, this work was carried out in our own department, and we were well aware of it.  Thus our surprise with the review, since to say that our work is a repeat of Amy Hoeksema's work is so inaccurate as to make us wonder whether the reviewer understood what we propose to do.  On October 11th, 2016, we sat down with Max Morris to discuss the similarities and differences between the Hoeksema U-statistic, and the methods used and features derived in our paper. Max was at least as surprised as we were to read the reviewer's comment, since the differences between Amy's work and ours are stark. The Hoeksema U-statistic characterizes toolmark signatures by producing two sets of correlation values. One set is produced by doing "coordinated shifts" after finding the ideal matching window, and computing each correlation value. The other set is computed by doing "independent shifts". When the two toolmarks match, we'd expect that the correlation values from the coordinated shifts would be significantly higher than those computed from the independent shifts, and this is assessed using a Mann-Whitney U statistic. While very interesting and worth further discussion, Max Morris agreed that this is far different from the methods we have proposed. In our work, we use full bullet signatures from pairs of bullets and extract several features based on these. The features include a cross-correlation, as well as the number of matching striae, the number of consecutive matching striae, the difference in the height of the signatures at each peak and at each valley, and several more. At no time is a Mann-Whitney U statistic used, windows extracted, or any coordinated/independent shifts used. These are completely different approaches where the only "similarity" is that we also compute a correlation, albeit between different variables!**

@@

    **The reviewer must have looked at the wrong code because no one who is reasonably familiar with R would claim that x3prplus is a "wrapper" for x3pr!  Please see the attached document for a rebuttal to these claims.  In x3prplus, all we did is call ONE of Petraco's functions, read.x3p, to read 3D files.  Everything else is completely different, as can be seen in the attached document. Perhaps our choice of name for the package has contributed to the confusion. Therefore, we have written our own function to read x3p files and have renamed our new package bulletr. bulletr is completely separate from x3pr and has many more capabilities.**

@@

    **Really?  We have referred to many of those papers in the manuscript and have shown how our approach is quite different.  Indeed, even PCAST (the President's Council of Advisors in Science and Technology) in its report, mentioned that our work was the only promising approach and they actually looked at all the literature themselves. So we respectfully disagree with Reviewer 2. The Riva and Champod paper published in 2014 is indeed referred to in the manuscript and of all the published work, it is the one that most resembles what we have done.  The reviewer poo-poos our saying that one difference is that Riva and Champod worked on casings and we worked on bullets.  The reviewer would be well advised to read our comment more carefully;  the reason it is important is that Riva and Champod make use of the circular structure of their data to pre-process their images and develop their score.  A big component of their algorithm is the alignment of images, which they do by rotating the images on the XY plane.  This is not something that can be extended to the case of bullets, were the XY plane is not flat and where rotation makes no sense.  The approach they use to extract features from the aligned images is completely different from ours and for the reviewer to say that we are re-inventing the wheel is a bit of a scandal.  The fact that Riva and Champod have come up with a nice automated algorithm to match breech face and firing pin images does not mean that we cannot come up with a DIFFERENT automated algorithm to match bullet lands. This said, we have added additional commentary about Riva and Champod in our manuscript.**

@@

    **We referenced the OpenFMC organization and devoted a paragraph to its discussion. This is the organization that is the recommended citation for the package which we use a function of, `x3pr`. We have added a reference to Dr. Petraco directly in this discussion. See the below citation, given by `x3pr` as of October 17th, 2016:**

    ```{r}
    citation("x3pr")
    ```

    **However, in the end we decided to go a step further and completely remove the dependency on Petraco's code. Right now, we are not using *any* of Petraco's code in any of our functions.**

@@

    **We are very clear about the limitations presented by a small dataset, particularly in the conclusion. Unfortunately, this are the data that we had to work with. With that said, the idea of statistical modeling is that once new data are obtained, it will be rather trivial to compute the set of features used in our model, and retrain the model with a broader and more varied dataset. Whether performance on holdout samples would remain as strong remains to be seen. But because this code is open-source and in the public domain, the algorithm can be assessed on new data by anyone willing to invest the time to run it. While the dataset is small (only 10 barrels) we have been told by multiple firearm examiners that it is a challenging dataset on which to develop methods because the 10 barrels were consecutively manufactured. Thus, one would expect that the striae made by those barrels will be more similar across them than across two randomly selected barrels from a large population. We are collaborating with Alan Zhang in NIST to assemble a larger database that will be publicly available within a year or two.**

@@

    **Did the reviewer read the correct paper?  The copy of our paper that we sent out for revision contains over thirty references, not just one. Many are from previous statistical studies on bullet matching (e.g., Biasotti 1959, Chu 2010, Riva 2014) while many more are references on statistical tests themselves (e.g., Therneau 2015, Liaw 2002, Cleveland 1979)**

@@

# bulletr - January 2017

The three reviewers that were brought in for the second round of reviews based many of their criticisms on our allged "lifting" of Petraco's code. Nothing could be further from reality.  Our original package x3prplus only made use of a single function in Petraco's x3pr package, that was used to read in the 3D data files.  The rest of our package shares absolutely nothing else with Petraco's as explained below.  The differences are so clear, that perhaps one reviewer could have been confused; but to have three reviewers make the exact same completely inaccurate accusation seems more like a coordinated effort to undermine our work.

Regardless, we have decided that we do not wish to rely on Petraco's package at all. Toward this end, we have written our own function to read in 3D files (which does not have any similarity with Petraco's read.x3p function) and have renamed our new package bulletr.  In this way, we no longer share a single line of code with Petraco.

# x3prplus - October 2016
